---
title: "RT mean plots- ERP-Fix"
author: "Hannah"
date: "8/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, out.width = "50%", out.height = "50%")
library(lme4)
library(lmerTest)
library(dplyr)
library(knitr)
library(kableExtra)
library(ggplot2)
library(ggpubr)
library(cowplot)


dat = read.delim("AllSubs_acceptedTrials_long_nobe_nobs_withRT_meancenteredP2.txt")
```

## 1. RTs
### Race categorization  
DV is trial level RT. Incorrect trials and trials with +/- 75 uV artifacts are excluded. Subjects with < 50% trials accepted are excluded (subs 32, 51 and 62).

Total sample n = 65  
Included n = 62

```{r}
# Add predictors, effect coding
dat$TarRace.e = -1
dat$TarRace.e[dat$Race == "White"] = 1

dat$Fix.e = -1
dat$Fix.e[dat$Fix == "forehead"] = 1

# model specification
# lmer(RT ~ 1 + (TarRace.e*Fix.e|Subject), data = dat) %>%  summary() #use this

m1 = lmer(RT ~ TarRace.e*Fix.e + (TarRace.e+Fix.e|Subject), data = filter(dat, Electrode == "CZ")) #only need one observation per trial

# check convergence issue
 # relgrad <- with(m1@optinfo$derivs,solve(Hessian,gradient))
 # max(abs(relgrad)) # since this value is really small, model is ok
 
sum.m1 = summary(m1)
sum.m1$call
sum.m1$varcor
kable(round(sum.m1$coefficients, digits=3)) %>% 
  kable_styling(full_width = F, position = "center")

rts = filter(dat, Electrode == "CZ") %>% 
  select(RT, Race, Fix) %>% 
  group_by(Race, Fix) %>% 
  summarise_all(list(RTmean = mean)) %>% 
  as.data.frame()

sds = filter(dat, Electrode == "CZ") %>% 
  select(RT, Race, Fix) %>% 
  group_by(Race, Fix) %>% 
  summarise_all(list(RTsd = sd)) %>% 
  as.data.frame() 

kable(cbind(rts, sds[3])) %>% 
  kable_styling(full_width = F, position = "center")


# bar graph
ggplot(dat, aes(Race, RT, fill = Fix)) +
  stat_summary(fun.y = mean, geom = "bar", position = "dodge") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .2) +
  labs(y = "Reaction Time", x = "Target Race") +
  scale_fill_manual(values=c("black","grey70"), guide = guide_legend(title = "Fixation")) +
  theme_bw() +
  ggtitle("Race task") +
  coord_cartesian(ylim = c(400, 500)) +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        strip.text.x = element_text(face = "bold", size = 14),
        strip.background = element_rect(fill = "grey98"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        plot.title = element_text(hjust = 0.5))

```


## 2. P2 amp
### Race categorization  
DV is trial level P2. Incorrect trials and trials with +/- 75 uV artifacts are excluded. Subjects with < 50% trials accepted are excluded (subs 32, 51 and 62).

Total sample n = 65  
Included n = 62

```{r}
# model specification
# lmer(MeanAmp ~ 1 + (TarRace.e*Fix.e|Subject) + (1|Elctrode), data = dat) %>%  summary()

m1 = lmer(MeanAmp ~ TarRace.e*Fix.e + (TarRace.e*Fix.e|Subject) + (1|Electrode), data = dat) #only need one observation per trial

# check convergence issue
 # relgrad <- with(m1@optinfo$derivs,solve(Hessian,gradient))
 # max(abs(relgrad)) # since this value is really small, model is ok
 
sum.m1 = summary(m1)
sum.m1$call
sum.m1$varcor
kable(round(sum.m1$coefficients, digits=3)) %>% 
  kable_styling(full_width = F, position = "center")
```
