---
title: "Mean analysis: Race-Gen"
author: "Hannah"
date: "11/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, out.width = "50%", out.height = "50%")
library(lme4)
library(lmerTest)
library(dplyr)
library(knitr)
library(kableExtra)
library(ggplot2)
library(ggpubr)
library(cowplot)


dat = read.delim("AllSubs_acceptedTrials_long_nobe_nobs_withRT_meancenteredP2.txt")
```

## 1. RTs

### 1a. Gender categorization task
DV is trial level data. Incorrect trials and trials with +/- 75 uV artifacts are excluded. Subjects with < 50% trials accepted are excluded. 

Included n = 63 (32 black, 31 white)

```{r}
gendat = filter(dat, Task == "Gender")

# Add predictors, effect coding
gendat$TarRace.e = -1
gendat$TarRace.e[gendat$TarRace == "White"] = 1

gendat$TarGender.e = -1
gendat$TarGender.e[gendat$TarGender == "male"] = 1

gendat$ParRace.e = -1
gendat$ParRace.e[gendat$ParRace == "White"] = 1

gendat$Fix.e = -1
gendat$Fix.e[gendat$Fix == "forehead"] = 1

# model specification
# lmer(RT ~ 1 + (TarRace.e*TarGender.e*Fix.e|Subject), data = gendat) %>%  summary()
# lmer(RT ~ 1 + (TarRace.e+TarGender.e+Fix.e|Subject), data = gendat) %>%  summary() # use this

m1 = lmer(RT ~ TarRace.e*TarGender.e*Fix.e*ParRace.e + (TarRace.e+TarGender.e+Fix.e|Subject), data = gendat)

# check convergence issue
 # relgrad <- with(m1@optinfo$derivs,solve(Hessian,gradient))
 # max(abs(relgrad)) # since this value is really small, model is ok

sum.m1 = summary(m1)
sum.m1$call
sum.m1$varcor
kable(round(sum.m1$coefficients, digits=3)) %>% 
  kable_styling(full_width = F, position = "center")

rts = filter(gendat, Electrode == "CZ") %>% 
  select(RT, TarRace, TarGender, Fix, ParRace) %>% 
  group_by(TarRace, TarGender, Fix, ParRace) %>% 
  summarise_all(list(RTmean = mean)) %>% 
  as.data.frame()

sds = filter(gendat, Electrode == "CZ") %>% 
  select(RT, TarRace, TarGender, Fix, ParRace) %>% 
  group_by(TarRace, TarGender, Fix, ParRace) %>% 
  summarise_all(list(RTsd = sd)) %>% 
  as.data.frame()

kable(cbind(rts, sds[5])) %>% 
  kable_styling(full_width = F, position = "center")
```

See markdown code for breaking down interactions.
```{r, eval=F}
m1.b = lmer(RT ~ TarRace.e*TarGender.e*Fix.e + (TarRace.e+TarGender.e+Fix.e|Subject), data = filter(gendat, ParRace == "Black"))
m1.w = lmer(RT ~ TarRace.e*TarGender.e*Fix.e + (TarRace.e+TarGender.e+Fix.e|Subject), data = filter(gendat, ParRace == "White"))

m1.be = lmer(RT ~ TarRace.e*TarGender.e + (TarRace.e+TarGender.e|Subject), data = filter(gendat, ParRace == "Black" & Fix == "eyes"))
m1.bf = lmer(RT ~ TarRace.e*TarGender.e + (TarRace.e+TarGender.e|Subject), data = filter(gendat, ParRace == "Black" & Fix == "forehead"))

m1.simple = lmer(RT ~ TarRace.e*TarGender.e + (TarRace.e+TarGender.e|Subject), data = gendat)

```


```{r}
# bar graph
facet_labels = c(Black = "Black participants", White = "White participants")
ggplot(gendat, aes(TarRace, RT, fill = TarGender)) +
  stat_summary(fun.y = mean, geom = "bar", position = "dodge") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .2) +
  facet_wrap(~ParRace, labeller=labeller(ParRace = facet_labels)) + 
  ggtitle("Gender task: Collapsed across fixation") +
  labs(y = "Reaction Time", x = "Target Race") +
  scale_fill_manual(values=c("black","grey70"), guide = guide_legend(title = "Target Gender")) +
  theme_bw() +
  coord_cartesian(ylim = c(400, 500)) +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        strip.text.x = element_text(face = "bold", size = 14),
        strip.background = element_rect(fill = "grey98"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        plot.title = element_text(hjust = 0.5))

# separated by fixation
ggplot(gendat, aes(TarRace, RT, fill = TarGender)) +
  stat_summary(fun.y = mean, geom = "bar", position = "dodge") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .2) +
  facet_wrap(~ParRace*Fix, labeller=labeller(ParRace = facet_labels)) + 
  labs(y = "Reaction Time", x = "Target Race") +
  scale_fill_manual(values=c("black","grey70"), guide = guide_legend(title = "Target Gender")) +
  theme_bw() +
  ggtitle("Gender task") +
  coord_cartesian(ylim = c(400, 500)) +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        strip.text.x = element_text(face = "bold", size = 14),
        strip.background = element_rect(fill = "grey98"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        plot.title = element_text(hjust = 0.5))

```

### 1b. Race categorization task

DV is trial level data. Incorrect trials and trials with +/- 75 uV artifacts are excluded. Subjects with < 50% trials accepted are excluded. 

Included n = 63 (33 black, 30 white)

```{r}
racedat = filter(dat, Task == "Race")

# Add predictors, effect coding
racedat$TarRace.e = -1
racedat$TarRace.e[racedat$TarRace == "White"] = 1

racedat$TarGender.e = -1
racedat$TarGender.e[racedat$TarGender == "male"] = 1

racedat$ParRace.e = -1
racedat$ParRace.e[racedat$ParRace == "White"] = 1

racedat$Fix.e = -1
racedat$Fix.e[racedat$Fix == "forehead"] = 1

# model specification
# lmer(RT ~ 1 + (TarRace.e*TarGender.e|Subject), data = racedat) %>%  summary()
# lmer(RT ~ 1 + (TarRace.e+TarGender.e|Subject), data = racedat) %>%  summary() # use this

m2 = lmer(RT ~ TarRace.e*TarGender.e*ParRace.e*Fix.e + (TarRace.e+TarGender.e+Fix.e|Subject), data = racedat)

sum.m2 = summary(m2)
sum.m2$call
sum.m2$varcor
kable(round(sum.m2$coefficients, digits=3)) %>% 
  kable_styling(full_width = F, position = "center")

rts = filter(racedat, Electrode == "CZ") %>% 
  select(RT, TarRace, TarGender, Fix, ParRace) %>% 
  group_by(TarRace, TarGender, Fix, ParRace) %>% 
  summarise_all(list(RTmean = mean)) %>% 
  as.data.frame()

sds = filter(racedat, Electrode == "CZ") %>% 
  select(RT, TarRace, TarGender, Fix, ParRace) %>% 
  group_by(TarRace, TarGender, Fix, ParRace) %>% 
  summarise_all(list(RTsd = sd)) %>% 
  as.data.frame()

kable(cbind(rts, sds[5])) %>% 
  kable_styling(full_width = F, position = "center")
```
See markdown code for breaking down interactions.
```{r, eval=F}
m2.b = lmer(RT ~ TarRace.e*TarGender.e*Fix.e + (TarRace.e+TarGender.e+Fix.e|Subject), data = filter(racedat, ParRace == "Black"))
m2.w = lmer(RT ~ TarRace.e*TarGender.e*Fix.e + (TarRace.e+TarGender.e+Fix.e|Subject), data = filter(racedat, ParRace == "White"))

m2.we = lmer(RT ~ TarRace.e*TarGender.e + (TarRace.e+TarGender.e|Subject), data = filter(racedat, ParRace == "White" & Fix == "eyes"))
m2.wf = lmer(RT ~ TarRace.e*TarGender.e + (TarRace.e+TarGender.e|Subject), data = filter(racedat, ParRace == "White" & Fix == "forehead"))

m2.be = lmer(RT ~ TarRace.e*TarGender.e + (TarRace.e+TarGender.e|Subject), data = filter(racedat, ParRace == "Black" & Fix == "eyes"))
m2.bf = lmer(RT ~ TarRace.e*TarGender.e + (TarRace.e+TarGender.e|Subject), data = filter(racedat, ParRace == "Black" & Fix == "forehead"))


m2.simple = lmer(RT ~ TarRace.e*TarGender.e + (TarRace.e+TarGender.e|Subject), data = racedat)
```


```{r}
# bar graph
facet_labels = c(Black = "Black participants", White = "White participants")
ggplot(racedat, aes(TarRace, RT, fill = TarGender)) +
  stat_summary(fun.y = mean, geom = "bar", position = "dodge") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .2) +
  facet_wrap(~ParRace, labeller=labeller(ParRace = facet_labels)) + 
  #  ggtitle("Total number of errors") +
  labs(y = "Reaction Time", x = "Target Race") +
  scale_fill_manual(values=c("black","grey70"), guide = guide_legend(title = "Target Gender")) +
  theme_bw() +
  ggtitle("Race task") +
  coord_cartesian(ylim = c(400, 500)) +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        strip.text.x = element_text(face = "bold", size = 14),
        strip.background = element_rect(fill = "grey98"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        plot.title = element_text(hjust = 0.5))

# separated by fixation
ggplot(racedat, aes(TarRace, RT, fill = TarGender)) +
  stat_summary(fun.y = mean, geom = "bar", position = "dodge") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .2) +
  facet_wrap(~ParRace*Fix, labeller=labeller(ParRace = facet_labels)) + 
  #  ggtitle("Total number of errors") +
  labs(y = "Reaction Time", x = "Target Race") +
  scale_fill_manual(values=c("black","grey70"), guide = guide_legend(title = "Target Gender")) +
  theme_bw() +
  ggtitle("Race task") +
  coord_cartesian(ylim = c(400, 500)) +
  theme(panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        strip.text.x = element_text(face = "bold", size = 14),
        strip.background = element_rect(fill = "grey98"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        plot.title = element_text(hjust = 0.5))

```

## 2. Mean P2 amplitude

### 1a. Gender categorization task
DV is trial level data. Incorrect trials and trials with +/- 75 uV artifacts are excluded. Subjects with < 50% trials accepted are excluded. 

Included n = 63 (32 black, 31 white)

```{r}

m1 = lmer(value ~ TarRace.e*TarGender.e*Fix.e*ParRace.e + (TarRace.e+TarGender.e+Fix.e|Subject), data = gendat)

# check convergence issue
 # relgrad <- with(m1@optinfo$derivs,solve(Hessian,gradient))
 # max(abs(relgrad)) # since this value is really small, model is ok

sum.m1 = summary(m1)
sum.m1$call
sum.m1$varcor
kable(round(sum.m1$coefficients, digits=3)) %>% 
  kable_styling(full_width = F, position = "center")

```

See markdown code for breaking down interactions.
```{r, eval=F}
m1.e = lmer(value ~ TarRace.e*TarGender.e + (TarRace.e+TarGender.e|Subject), data = filter(gendat, Fix == "eyes"))

lmer(value ~ TarGender.e + (TarRace.e|Subject), data = filter(gendat, Fix == "eyes" & TarRace == "Black")) %>% summary()
lmer(value ~ TarGender.e + (TarRace.e|Subject), data = filter(gendat, Fix == "eyes" & TarRace == "White")) %>% summary()

m1.f = lmer(value ~ TarRace.e*TarGender.e + (TarRace.e+TarGender.e|Subject), data = filter(gendat, Fix == "forehead"))


```

### 1b. Race categorization task

DV is trial level data. Incorrect trials and trials with +/- 75 uV artifacts are excluded. Subjects with < 50% trials accepted are excluded. 

Included n = 63 (33 black, 30 white)

```{r}

m2 = lmer(value ~ TarRace.e*TarGender.e*ParRace.e*Fix.e + (TarRace.e+TarGender.e+Fix.e|Subject), data = racedat)

# check convergence issue
 # relgrad <- with(m1@optinfo$derivs,solve(Hessian,gradient))
 # max(abs(relgrad)) # since this value is really small, model is ok

sum.m2 = summary(m2)
sum.m2$call
sum.m2$varcor
kable(round(sum.m2$coefficients, digits=3)) %>% 
  kable_styling(full_width = F, position = "center")

```

Breaking down interactions:
```{r}
rts = filter(racedat, Electrode == "CZ") %>%
  filter(Subject != 28) %>% # NA values
  select(value, TarRace, TarGender, Fix) %>% 
  group_by(TarRace, TarGender, Fix) %>% 
  summarise_all(list(P2mean = mean)) %>% 
  as.data.frame()


```

*Eyes fixation:*  
```{r}
lmer(value ~ TarRace.e*TarGender.e + (TarRace.e+TarGender.e|Subject), data = filter(racedat, Fix == "eyes")) %>% summary()
```
Black faces:  
```{r}
lmer(value ~ TarGender.e + (TarRace.e|Subject), data = filter(racedat, Fix == "eyes" & TarRace == "Black")) %>% summary()
```
White faces:  
```{r}
lmer(value ~ TarGender.e + (TarRace.e|Subject), data = filter(racedat, Fix == "eyes" & TarRace == "White")) %>% summary()
```

*Forehead fixation:*  
``` {r}
lmer(value ~ TarRace.e*TarGender.e + (TarRace.e+TarGender.e|Subject), data = filter(racedat, Fix == "forehead")) %>% summary()
```
Black faces:  
```{r}
lmer(value ~ TarGender.e + (TarRace.e|Subject), data = filter(racedat, Fix == "forehead" & TarRace == "Black")) %>% summary()
```
White faces:  
```{r}
lmer(value ~ TarGender.e + (TarRace.e|Subject), data = filter(racedat, Fix == "forehead" & TarRace == "White")) %>% summary()
```
